Evidence for a Third Color Parameter Within the Type~Ia Supernovae of the Nearby Supernova Factory

### 2018-09-28 submit/fix.tex
changes of Ariel

\documentclass{aastex62}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{natbib}
\usepackage{lineno}
\usepackage{color}
\defcitealias{1999PASP..111...63F}{F99}
\defcitealias{2017ApJ...842...93M}{M17}
\linenumbers

@@

Even two parameters are probably not enough to capture supernova color diversity.  SNe~Ia 
are affected by interstellar Milky Way-like dust  and by ``intrinsic'' color variations from the supernova itself and its surrounding circumstellar dust. Physical modeling
shows that the complexity of interstellar dust shouldn't be expected to be captured by a single parameter \citep{2015ApJ...807L..26G,
2017ApJ...836...13H}. Supernova models \citep[e.g.][]{2007ApJ...662..487W,2013MNRAS.436..333S,2014MNRAS.441..532D,2015MNRAS.454.2549B,
2017ApJ...846...58H} and circumstellar dust \citep{2005ApJ...635L..33W,
2008ApJ...686L.103G} produce color variations beyond those due to interstellar dust.  A third color
parameter is therefore expected.

>>>>

\documentclass[trackchanges]{aastex62}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{natbib}
\usepackage{lineno}
\usepackage{color}
\defcitealias{1999PASP..111...63F}{F99}
\defcitealias{2017ApJ...842...93M}{M17}
\linenumbers

@@

Even two parameters are probably not enough to capture supernova color diversity.  SNe~Ia 
are affected by interstellar Milky Way-like dust  and by ``intrinsic'' color variations from the supernova itself and its surrounding circumstellar dust. Physical modeling
shows that the complexity of interstellar dust shouldn't be expected to be captured by a single parameter \citep{2015ApJ...807L..26G,
2017ApJ...836...13H}. Supernova models \citep[e.g.][]{2007ApJ...662..487W,2013MNRAS.436..333S,2014MNRAS.441..532D,2015MNRAS.454.2549B,
2017ApJ...846...58H} and circumstellar dust \citep{2005ApJ...635L..33W,
2008ApJ...686L.103G} produce
color variations beyond those due to interstellar dust. 
\added{
\citet{doi:10.1093/mnras/sty1619} report time-variation in apparent dust properties
though \citet{2017ApJ...850...84H} argue that the expected observational effect of the non-uniform ISM should be weak.
}
A third color
parameter is therefore expected.
